---
title: "dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

# Creating flex_dashboard
Put dashboard on desktop, not in repo with webpage - this is related to YML later

to create, go to new R Markdown, from template, and then Flexdashboard
output is a little different, but it is still fundamentally R Markdown
`{data-width}` lets you specify the width each element takes up 
General steps - have a code chunk to install packages (does not show), have another code chunk to import and clean data (also does not show), then you have your columns to display your actual data/plots on the dashboard

Can you make it so all the graphs change together when you filter by a neighborhood?
Yes, but it's tough - need Shiny and brushing technique

The problem with putting dashboard in website repo is that it will import all the formatting from the site YML, overwriting all the desired formatting you wanted
To circumvent, in console, do `rmarkdown::render("dashboard.Rmd", output_format = "flexdashboard::flex_dashboard")`
Including your dashboard on a website usually requires one additional step
Alternatively, can just rebuild your website (build tab that opens on right side, and clicking build website) and it should work even without the console command

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(p8105.datasets)
```

```{r}
data("nyc_airbnb")

nyc_airbnb <- 
  nyc_airbnb |> 
  mutate(rating = review_scores_location/2) |>
  select(
    rating, neighbourhood_group, neighbourhood,
    room_type, lat, long, price
  ) |> 
  drop_na(rating) |> 
  filter(
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500
  )
```

Use plotly to make some plots 

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}
nyc_airbnb |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  plot_ly(
    x = ~neighbourhood,
    y = ~price, 
    color = ~neighbourhood,
    type = "box"
  )
```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}
nyc_airbnb |> 
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating))  |> 
  plot_ly(
    x = ~lat, y = ~long, color = ~price, text = ~text_label,
    type = "scatter", mode = "markers"
  )
```

### Chart C

```{r}
nyc_airbnb |> 
  count(neighbourhood) |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) |> 
  plot_ly(
      x = ~neighbourhood,
      y = ~n,
      type = "bar"
  )
```

